\huge Tor's Usability for Censorship Circumvention

### 2016-04-23 pets2017-paper/pets2017-paper.tex
It was about Tor Browser 4.5 that our uxsprint2015 changes started happening.
Previously this said "Tor Browser 5.1," which is not a version number
that existed.

Here's an example of one of our tagged tickets getting closed in the Tor
Browser changelog. 4.5a4 is earlier than 4.5, but maybe we should just
mention the stable release.

https://gitweb.torproject.org/builders/tor-browser-bundle.git/tree/Bundle-Data/Docs/ChangeLog.txt
Tor Browser 4.5a4 -- Feb 24 2015
     * Bug 14630: Hide Torbutton's proxy settings tab.

There have been been no published usability evaluations of
Tor Browser since the 3.5 series, which introduced radical UI changes~\cite{torbrowser-35}.
The most recent usability effort is an unpublished pilot study by Lee and Fifield~\cite{uxsprint} 
that tested the downloading, installation, and browsing tasks in Tor Browser.  This study uncovered a number of issues~\cite{uxsprint2015-tickets},
some of which influenced changes in Tor Browser version~5.1 and later.

@@

\section{Future Work} 
Throughout the qualitative user study, redesign of the interface, and the quantitative user study, we collaborated and communicated with Tor developers. Redesigning the configuration interface was a mutual interest. In fact, Tor version {\color{red} 5.?.?} incorporated textual and navigational changes based on our redesigned interface. We plan to work with Tor developers to integrate helpful changes. This process will entail debugging our code, merging changes with the current version of Tor, making high-fidelity graphics that align with style guides, and finalizing the advice to give to users in the interface.

>>>>

There have been been no published usability evaluations of
Tor Browser since the 3.5 series, which introduced radical UI changes~\cite{torbrowser-35}.
The most recent usability effort is an unpublished pilot study by Lee and Fifield~\cite{uxsprint} 
that tested the downloading, installation, and browsing tasks in Tor Browser.  This study uncovered a number of issues~\cite{uxsprint2015-tickets},
some of which influenced changes in Tor Browser version~4.5 and later.

@@

\section{Future Work} 
Throughout the qualitative user study, redesign of the interface, and the quantitative user study, we collaborated and communicated with Tor developers. Redesigning the configuration interface was a mutual interest. In fact, Tor version~4.5 incorporated textual and navigational changes based on our redesigned interface. We plan to work with Tor developers to integrate helpful changes. This process will entail debugging our code, merging changes with the current version of Tor, making high-fidelity graphics that align with style guides, and finalizing the advice to give to users in the interface.
